### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon - Enthalpy - added tables of the enthalpy values at each Tx

>>>>

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ \\ 
		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
		\midrule
		100  & 59.59 & 6.97 & 49.16 & 22.84 & 46.08 \\
		80   & 42.61 & 6.08 & 32.33 & 18.27 & 31.25 \\
		60   & 30.02 & 4.05 & 25.41 & 16.76 & 19.81 \\
		40   & 16.93 & 4.36 & 12.44 & 11.13 & 11.68 \\
		30   & 12.03 & 3.68 & 9.32  & 9.18  & 9.02  \\
		20   & 7.18  & 2.21 & 4.99  & 5.67  & 5.78  \\
		15   & 5.48  & 2.01 & 3.65  & 4.69  & 4.43  \\
		10   & 3.45  & 1.43 & 2.28  & 3.14  & 2.92  \\
		5    & 1.65  & 0.69 & 1.09  & 1.47  & 1.42  \\
		\bottomrule
	\end{tabular}
	\caption{Bulk \MgZnCa~ alloy \gls{h} of crystallisation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}; \gls{h} is in $J/g$.}
	\label{tab:Bulk_Enthalpy}
\end{table}

\begin{table}[h]
	\centering
	\begin{tabular}{ c c c c c c }
		\toprule
		Heating Rate \acrshort{ht} & $h_{T_{x1}}$ & $h_{T_{x2}}$ & $h_{T_{x3}}$ & $h_{T_{x4}}$ & $h_{T_{x5}}$ \\ 
		$K/min$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ & $J/g$ \\
		\midrule
		100  & 48.24 &    & 49.85 &    & 43.38 \\
		80   & 43.27 &    & 53.56 &    & 36.18 \\
		60   & 15.5  &    & 8.78  &    & 22.4  \\
		40   & 16.22 &    & 9.13  &    & 16.27 \\
		30   & 13.72 &    & 7.16  &    & 11.81 \\
		20   & 6.16  &    & 2.3   &    & 7.45  \\
		15   & 6.99  &    & 3.66  &    & 6.57  \\
		\bottomrule
	\end{tabular}
	\caption{Film \MgZnCa~ alloy \gls{h} of crystallisation for $Tx_{1-5}$ for the various \acrshort{dsc} \acrlongpl{ht} \acrshort{ht}; \gls{h} is in $J/g$.}
	\label{tab:Film_Enthalpy}
\end{table}
